
\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	12pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{fontspec}
% \usepackage{ebgaramond} % Use the EB Garamond font
\setmainfont{EB Garamond}
\newenvironment*{coverhead}[3]{
    \today

    #1
    
    #2

    Dear #3,}{}

\name{Khoi Nguyen} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{\href{tel:4372257746}{(437)~$\cdot$~225~$\cdot$~7746} \\ \href{mailto:bob.k.nguyen@gmail.com}{bob.k.nguyen@gmail.com} \\ \href{https://linkedin.com/in/mnkhoi}{linkedin.com/in/mnkhoi} \\ \href{https://github.com/mnkhoi}{github.com/mnkhoi} \\ \href{https://mnkhoi.com}{mnkhoi.com}} % Contact information
%----------------------------------------------------------------------------------------
\begin{document}
    \medskip
    \hrule % Horizontal rule
    \medskip
    \coverhead{Twilio}{}{Hiring Manager}
    
    I am excited to apply for the Software Engineer opportunity in Twilio Engineering's team as seen on the company's job board. I am currently a fourth-year Computer Science specialist at the University of Toronto. From my studies so far, I have learnt a strong understanding of object-oriented programing, data structures and computer infrastructure, and am looking forward to learning about new technologies to improve myself. As someone who is interested in exploring new technologies that pushes the limit, Twilio is the perfect as it values innovation and includes diversity. The Software Engineering position would allow me to build upon what I have learnt at school while contributing my knowledge, skills, and unique outlook to help drive innovation in your company.

    During my time interning at AMD, I was able to apply my knowledge of programming languages and technologies, including Ruby, Golang, Typescript, Node.js, C++ and SQL, to assist in developing tooling for the SOC DV infrastructure team. In addition, I had the opportunity to bring up new project initiatives such as LSF Monitor that can help greatly improve the developer experience in the team. And an organization chart with roles and permissions services for the current tools that we have as the team grows.

    % During my time interning at the Nexle, I was able to apply my knowledge of programming languages and technologies, including HTML, CSS, Javascript, React, Redux, Node.js, SQL and MySQL, to assist in developing content management systems for the companies clients. In addition, I had the opportunity to join a Scrum team and experience Agile methodology which gave me a better understanding of project management and significantly improved my communication. When the team was asked to redesign the database and back-end, I proposed an improvement in the relationships between objects. As a result, it improves the speed of the back-end and reduces confusion for developers in the team.

    In addition to my technical knowledge, I can bring effective communication and innovative ideas. In my role as a Tech Associate at the Mathematical, Computer Science, and Statistic Academic Society,  I organized the Deer Hacks hackathon that had over 300 participants and 50 entries. Through this experience, I was able to effectively implement my creative ideas in the inner workings of the hackathon. I hope to provide the same ideas and professionalism as an Software Engineer at your company.

    I am an innovative problem-solver, effective communicator and curious learner, eager to take on new challenges and contribute to Twilio's mission. Thank you for taking the time to review my application. I look forward to hearing from you and can be contacted via email (\href{mailto:bob.k.nguyen@gmail.com}{bob.k.nguyen@gmail.com}) to discuss this new graduate position in further detail.

    Sincerely,

    Khoi Nguyen
\end{document}
